### 2020-10-04 Analysis/Code/Paper.Rmd
Added the selection and variance effects.

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provide similar evidence for restaurants on Yelp. A more honest way for a firm to influence reviews is by assuming an active approach to review management, and to publicly respond to reviews published online. @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. In somewhat contradictory findings, @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to, while @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity, because consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether different kinds of promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a Groupon price promotion. They present evidence that customers attracted by the promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher, which can explain the reasons behind their dissatisfaction. Thus, the paper cautions against running price promotions in an attempt to poach new customers and improve the online reputation. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also find that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.

The present study contributes to this literature by providing novel evidence from a new market. I show that customers buying computer games are significantly more likely to leave positive reviews during discounts. More importantly, I go beyond the descriptive nature of the other papers in the literature, and show that firms leverage this fact to improve their reviews by giving discounts, thus providing evidence of a novel reputation management behavior. A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". However, this study also finds that books are more likely to solicit negative feedback when sold for free, which somewhat undermines the strategy. Similar to @ByersEtAl12, @Zegners17 argues that purchasers of free books differ from the purchasers of regular books in their observable characteristics, and explains the negativity of the reviews by the selection effect.

@@

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around US\$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD], Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.

@@

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review labels*, or bins, to each game. These labels\footnote{There are labels worse than "Negative", but they are rare, so I bin all of them into "Negative"} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each game, such as its name, price, and if the game is currently on a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of the Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main independent review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an omage to the masterfuly chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on, say sales, should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. More importantly, Steam Database offers a daily time series of prices and player activity for each game on Steam. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent player for each game on a daily basis. In other words, if on a particular day 10 people play the game every hour, except noon, when 13 people play the game simultaneously, then the recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the evolution of the review score for each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the path of the review score.

@@

Steam is home to more than 25,000 games that differ in their genres, prices, sales, release dates, frequency of updates, and other characteristics. Inevitably, an appropriate sample should be selected for the analysis. @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper. First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of the a big number of reviews from the review score calculation. While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible. In particular, only games that were released in this time period make it to the sample.

Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience. Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}. Unobserved quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales, because, say, a game that has just issued a major update might both upgrade to a better review label (because of the positive reception of the new content) and give a big discount to rekindle the interest of the players, but the discounting decision would not be influenced by the review transition. For the same reasons, I also drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content, and the update history is not a perfect way to monitor the updating activity. Finally, I drop few games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.

@@

The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average. The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score history. An example observation from the sample is given in Figure \ref{exampleGame}. For the majority of the games in the sample, the player count is the highest around the release date, and then it quickly fades away and oscillates around a smaller level. The player count also jumps when a discount is given, reflecting the influx of new players. Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist}.

@@

As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is important. A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages. There are
`r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
`r panel[discNew==T, .N]` discounts. Steam has a number of rules that regulate price promotions on its platform. A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount. A game can not go on discounts too frequently, and has to wait between four to six weeks
after a price promotion to be able to run a new one. The duration of a custom discount is restricted to be at least one full day, and at most two weeks. Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount. As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”. Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots. An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays. Figure \ref{seasonalSalesPeriods} (in the Appendix) shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving). Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale. Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.

@@

The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly. Recall that the review score is just the fraction of the positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in. Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release. On average across games, the standard deviation of the review score (out of one hundred) is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`, with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that. The score is only assigned once the game reaches 10 reviews, and one can see that 10 reviews is enough, on average, to keep the score stable. The distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, is, then, representative of the situation at other ages.

@@

Despite the relative rigidity of the review score, there is enough transitions between the review bins to make the analysis of pricing decisions by firms around such transitions possible. Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample. The number of unique games that have changed review labels in the data is `r transitions[, unique(ID)] %>% length`, and the number of transitions is `r transitions[, .N]`. Sometimes games switch their bins briefly, and go back soon after. The number of transitions that led to the game spending at least 7 days in the new bin is `r transitions[(is.na(dur) | dur >= 7), .N]`. Table \ref{mDiscountTable} describes the state of the games in the two weeks before their transitions. Discounting  does take place before the transitions, games transition at very different ages, but tend to have only a limited number of reviews by the time their review bin changes.

@@

Consider game \(i\) that is observed on a daily basis. On day \(t\)
the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on
that day, a number that is unobserved by the econometrician. Define
*active players* of this game, \(A_{it}\), to be the customers who have
already purchased the game and are still playing it, either because they have
not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) players on day \(t\), which is also not observed.
I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
\begin{equation}\label{activeProccess}
  A_{it} = A_{it-1} + B_{it} - E_{it}
\end{equation}

Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about
them in order to make progress.

@@

### Demand Parameters
The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
\begin{equation}
\mathbb{E}\left[A_{it}\,|\,A_{it-1}, x_{it} \right] = A_{it-1} + \lambda_i(1+x'_{it}\beta) - (1-\psi_i)A_{it-1} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta),
\end{equation} so the model implies the following regression equation
\begin{equation}\label{arrivalReg}
 A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
\end{equation}
with
\(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\). This model is
non-linear in parameters, because \(\lambda_i\) is not known and enters
the model multiplying \(\beta\), the parameters common to all games. If
not for this commonality in $\beta$, estimation of (\ref{arrivalReg}) would be
straightforwardly achieved by opening the parentheses and estimating
\begin{equation}\label{arrivalRegInd}
A_{it} = \lambda_i + \psi_i A_{it-1} + x'_{it}\beta_i + u_{it}
\end{equation}
using OLS on a game-by-game basis. This commonality is
essential, however, because one game in the sample typically does not exhibit enough variation in review labels to be able to identify the effect of upgrading the review tier on sales.

The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain the elasticities. Normally, a log transformation is used to achieve that. Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model
\begin{equation}\label{logReg}
\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}.
\end{equation}
This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs. Thus, the structural model I formulate confronts the estimation problem in a more “heads-up” way, and in that regard offers an improvement over @SorokinStevens20. I will contrast the results obtained by the two approaches in the results section, comparing a more detailed structural approach with a less precise, but a more easily implementable, log regression approach.

Another important reason for insisting on estimating the relative effects stems from the limitations of my data. Recall that the player count variable measures only the *maximum concurrent* number of active players every day. This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”. An implicit assumption in my analysis is that new buyers of the game all choose their gaming time following the same game-specific distribution. I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".

Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model \ref{arrivalReg}, and guarantees identification of all parameters, as long as there is sufficient variation in the data. Of course, this is only true as long as equation \ref{arrivalReg} is the right model of the data generating process. A threat to identification would come from unobserved demand shifters $\tilde x_{it}$ that are correlated with the observed factors $x_{it}$ (omitted variable bias). For instance, an advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price. My approach is vulnerable to such events, as long as one is interested in getting the causal estimate of the discount elasticity of demand.

However, I argue that (\ref{arrivalReg}) is an adequate specification, if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand. First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day. Of course, there are various things that a firm can do, that can, in a non-guaranteed fashion, affect this variable. But, as long as the major tools that a firm has access to are controlled for in the regression, the exogenous variation in the review variables is sufficient to identify the causal effect of reviews on sales.

>>>>

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provide similar evidence for restaurants on Yelp. A more honest way for a firm to influence reviews is by assuming an active approach to review management, and to publicly respond to reviews published online. @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to. In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity. The idea is that consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether different kinds of promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a Groupon price promotion. They present evidence that customers attracted by the promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher, which can explain the reasons behind their dissatisfaction. Thus, the paper cautions against running price promotions in an attempt to poach new customers and improve the online reputation. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.

My paper contributes to this literature in several ways. First, I present evidence from a market that was not previously studied in the literature, and confirm that reviews left on a price promotion are not favorable to businesses. Second, I show that, nevertheless, firms can successfully manage their online reputation through pricing, by going on a discount when they are close to upgrading their review tier. A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". However, this study also finds that books are more likely to solicit negative feedback when sold for free, which somewhat undermines the strategy. Similar to @ByersEtAl12, @Zegners17 argues that purchasers of free books differ from the purchasers of regular books in their observable characteristics, and explains the negativity of the reviews by the selection effect.

@@

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around US\$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD[], Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.

@@

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review labels*, or bins, to each game. These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each title, such as its name, price, and if the game is currently on a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an omage to the masterfuly chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on, say sales, should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. More importantly, Steam Database offers a daily time series of prices and player activity for each game on Steam. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent player for each game on a daily basis. In other words, if on a particular day 10 people play the game every hour, except noon, when 13 people play the game simultaneously, then the recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the review score of each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the evolution of the review score.

@@

Steam is home to more than 25,000 games that differ in their genres, prices, sales, release dates, frequency of updates, and other characteristics. Inevitably, an appropriate sample should be selected for the analysis. @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper. First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of a big number of reviews from the review score calculation. While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible. In particular, only games that were released in this time period make it to the sample.

Second, online multiplayer games and games that update frequently are dropped from the sample, as these are products whose quality is changing a lot over time\footnote{Games on Steam have blogs that allow them to share news about updates with the audience. I used these update announcements to measure the number of updates each game had. Games with more than 5 small updates in the sample were excluded. Publishing news about an update is voluntary, so it is possible that some games that continue to update after the release still made it to the sample.}. Unobserved dynamic quality would present a big obstacle to the identification of the effect of reviews on pricing decisions or sales. Consider a game that has just issued a major update. It is a great time for the firm to give a discount in order to rekindle the interest in the game. That update could also help the game transition to a better review tier, thanks to the positive reception of the new content. Thus, game updates could give rise to a correlation between discounting decisions and review transitions that is not causal. Given the fact that the update history is an imperfect way to monitor the update activity, I decided to be conservative and to eliminate as many potential updaters as I could. For that same reason I drop free games and games that are released in a beta-version (the so called “Early Access” program), as these products are likely to be adding new content. Finally, I drop games with a player count of less than four on their median day, as these games are simply very small, and the quality of their player count data is questionable.

@@

The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average. The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score. An example observation from the sample is given in Figure \ref{exampleGame}. For the majority of the games in the sample, the player count is the highest around the release date, and then it quickly fades away and oscillates around a smaller level. The player count also jumps when a discount is given, reflecting the influx of new players. Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist}.

@@

As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is in order. A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages. There are
`r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
`r panel[discNew==T, .N]` discounts. Steam has a number of rules that regulate price promotions on its platform. A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount. A game can not go on discounts too frequently, and has to wait between four to six weeks
after a price promotion to be able to run a new one. The duration of a custom discount is restricted to be at least one full day, and at most two weeks. Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount. As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”. Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots. An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays. Figure \ref{seasonalSalesPeriods} (in the Appendix) shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving). Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale. Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.

@@

The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly. Recall that the review score is just the fraction of positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in. Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release. On average across games, the standard deviation of the review score is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`  (out of one hundred), with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that. Given how little the review score changes after the first month, the distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, should be representative of the situation at other ages.

@@

Despite the relative rigidity of the review score, there is enough transitions between review bins to make the analysis of pricing decisions by firms around such transitions possible. Table \ref{tab:transitionMatrix} describes the transitions between review bins in the sample. The number of unique games that have changed review labels in the data is `r transitions[, unique(ID)] %>% length`, and the number of transitions is `r transitions[, .N]`. Sometimes games switch their bins briefly, and go back soon after. The number of transitions that led to the game spending at least 7 days in the new bin is `r transitions[(is.na(dur) | dur >= 7), .N]`. Table \ref{mDiscountTable} describes the state of the games in the two weeks before such transitions. Discounting  does take place before the transitions, games transition at very different ages, but tend to have accumulated only a limited number of reviews by the time their review tier changes.

@@

Consider game \(i\) that is observed on a daily basis. On day \(t\)
the game sells one copy to each of the \(B_{it}\) short-lived buyers that arrive on
that day, a number that is unobserved by the econometrician. Define
*active players* of this game, \(A_{it}\), to be the customers who have
already purchased the game and are still playing it, either because they have
not yet completed it or are not bored with it yet. This number  has an empirical counterpart in
the face of the player count variable, observable to the econometrician. The game loses \(E_{it}\) active players on day \(t\), which is also not observed.
I assume that, once a player stops playing the game, she never returns to it again. It is easy to see then that \(A_{it}\) follows the following process:
\begin{equation}\label{activeProccess}
  A_{it} = A_{it-1} + B_{it} - E_{it}
\end{equation}

Both the arrival of buyers and the exit of players are not observed, so some assumptions need to be made about these variables in order to make progress.

@@

The prediction of \(A_{it}\) that follows from (\ref{activeProccess}) takes the form of
\begin{equation}
\mathbb{E}\left[A_{it}\,|\,A_{it-1}, x_{it} \right] = A_{it-1} + \lambda_i(1+x'_{it}\beta) - (1-\psi_i)A_{it-1} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta),
\end{equation} so the model implies the following regression equation
\begin{equation}\label{arrivalReg}
 A_{it} = \psi_i A_{it-1} + \lambda_i(1+x'_{it}\beta) + u_{it},
\end{equation}
with
\(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\). This model is
non-linear in parameters, because \(\lambda_i\) is not known and enters
the model multiplying \(\beta\), the parameters common to all games. If
not for this commonality in $\beta$, estimation of (\ref{arrivalReg}) would be
straightforwardly achieved by opening the parentheses and estimating
\begin{equation}\label{arrivalRegInd}
A_{it} = \lambda_i + \psi_i A_{it-1} + x'_{it}\beta_i + u_{it}
\end{equation}
using OLS on a game-by-game basis. This commonality is
essential, however, because one game in the sample typically does not exhibit enough variation in review labels to be able to identify the effect of upgrading the review tier on sales.

The fact that $x'_{it}\beta$ multiplies the game fixed effect $\lambda_i$ allows me to estimate the dependence of quantity sold on price and reviews in relative terms, i.e., to obtain the elasticities. Normally, a log transformation is used to achieve that. Indeed, @SorokinStevens20 is able to estimate these elasticities with a within-estimator, using the following model
\begin{equation}\label{logReg}
\log A_{it} = \tilde\lambda_i + \tilde\psi_i \log A_{it-1} + x'_{it}\tilde \beta + u_{it}.
\end{equation}
This specification “controls” for the (log) number of continuing players in order to overcome the non-availability of direct sales data; however, it is the numbers of active players and buyers that are additive, not their logs, as (\ref{activeProccess}) and (\ref{arrivalReg}) highlight. Thus, the structural model I formulate confronts the estimation problem in a more “heads-up” way, and in that regard offers an improvement over @SorokinStevens20. I will contrast the results obtained by the two approaches in the results section, comparing a more detailed structural approach with a less precise, but a more easily implementable, log regression approach.

Another important reason for insisting on estimating the relative effects stems from the limitations of my data. Recall that the player count variable measures only the *maximum concurrent* number of active players every day. This implies that the estimated values of $\lambda_{it}$ would take into account only those new buyers who contribute to gaming activity during the “rush hour”. An implicit assumption in my analysis is that new buyers of the game choose their gaming time following some fixed game-specific distribution. I use this assumption to say that, if the number of new active players during rush hour goes up by 1%, then sales go up by 1% across all types of players,  not only among the "rush hour ones".

Another advantage of using equation (\ref{arrivalReg}) to estimate demand parameters from player count data comes from the fact that it allows each game to have its own continuation probability $\psi_i$. Two games could have the same observed median daily player count---say, ten people---but very different sales levels, if game one offers a lot of replayability and is played by the same ten people over and over again, and game two is played by new ten people every day. Intuitively, $\psi_i$ is identified by the rate of decay of the player count when it is far from its (slowly-changing) trend or average. Game release and discounts offer such events, when the player count spikes briefly due to all the new players who just bought the game; see example game in Figure \ref{exampleGame}.

Assumption \(\mathbb{E}\left[u_i\,|\,A_{it-1}, x_{it} \right] = 0\) holds by definition for Model (\ref{arrivalReg}), and guarantees identification of all parameters, as long as there is sufficient variation in the data. Of course, this is only true as long as equation (\ref{arrivalReg}) is the right model of the data generating process. A threat to identification would come from unobserved demand shifters $\tilde x_{it}$ that are correlated with the observed factors $x_{it}$ (omitted variable bias). For instance, an unobserved advertising intervention that is coupled with a price promotion would increase demand, but the entire effect would be attributed to the observed change in price. My approach is vulnerable to such events, as long as one is interested in getting the causal estimate of the discount elasticity of demand.

However, I argue that (\ref{arrivalReg}) is an adequate specification if the goal is to estimate the causal effect of reviews on sales, or to get a predictive model of demand. First and foremost, the reviews are not a choice variable of a firm, and rather serve as a state variable that a firm takes as given every day. Of course, there are various things that a firm can do, that can, in a non-guaranteed fashion, affect this variable. But, as long as the major tools that a firm has access to are controlled for in the regression, the exogenous variation in the review variables is sufficient to identify the causal effect of reviews on sales.

The most direct way in which I control for firm behavior is by including the price in the set of explanatory variables. Any intervention that is correlated with discounts will be attributed to the price variable. The second important way in which I control for various tools that firms have at their disposal is through sample selection. Sample selection rules out the possibility of an omitted variable bias stemming from a number of variables that could collectively be referred to as “changing quality”. The games in the sample are single player games, and thus are not subject to time-varying network externalities or frequent quality updates that could be correlated with reviews, depths of discounts, or the player count. Third, game specific effect $\lambda_i$ controls for all time-invariant characteristics of game $i$ that determine average sales: initial marketing budget, extraneous popularity of the game's plot or setting, etc. Similarly, I employ a set of time effects to control for important within-week seasonality in gaming patterns and for the extensive platform-wide sales.
